Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-02 paper.qmd
Added langevitour plot for dens cluster

@@

scaled_c_shaped_data_model <- scaled_c_shaped |>
  filter(type == "model") |>
  select(-type)

>>>>

```{r}
#| label: prep-proj-one-dens-clust

@@

scaled_c_shaped_data_model <- scaled_c_shaped |>
  filter(type == "model") |>
  select(-type)
```

data_c_shaped_n <- data_c_shaped |>
  select(-type) |>
  mutate(type = factor(error_df_one_curvy_abs$error_cat_n2,
                          levels=c("low", "high")))

df_model_data_n <- bind_rows(df_bin_dens_clust, data_c_shaped_n)

langevitour::langevitour(df_model_data_n[1:(length(df_model_data_n)-1)],
                         lineFrom = distance_df_small_edges_c_shaped_structure$from,
                         lineTo = distance_df_small_edges_c_shaped_structure$to,
                         group = factor(df_model_data_n$type,
                                        c("low", "high", "model")),
                         levelColors = c('#d9d9d9', '#800026', "#000000"))
```
